\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{geometry}
\geometry{a4paper, margin=2cm}
\usepackage{amsmath}
\title{\textbf{Questions}}
\author{FPGAspeaks}
\date{August 2023}

\begin{document}

\maketitle

\section{Gate Questions}
\begin{enumerate}
    \item Given $F(a,b,c)=\sum m(3,6)$ write the function $F$ in boolean expression.
          \begin{flushright}
      (EC 2005)
    \end{flushright}
    \item A Boolean function $F$ of two variables is defined as follows: $F(0,0)=F(0,1)=F(1,1)=1$ and $F(1,0)=0$ write Boolean expression for $F$.\begin{flushright}
      (EC 2004)
    \end{flushright}
    \item In the sum of products function $F(x,y,z)=\sum m(2,3,4,5)$ write the function $F$ in boolean expression.
      \begin{flushright}
      (EC 2013)
    \end{flushright}
      \item Given $F(a,b,c,d)=\sum m(0,2,3,4,8,9,10)$ write the function $F$ in boolean expression.
          \begin{flushright}
      (EC 1998)
    \end{flushright}
    \item Given $F(a,b,c,d)=\sum m(0,2,8,10,11)+d(5,15)$ write the function $F$ in boolean expression.
          \begin{flushright}
      (EC 2006)
    \end{flushright}
    \item Write the simplified sum of products expression for Boolean function $F = m_0+m_2+m_3+m_5$, where $m_0, m_2, m_3, m_5$, are minterms corresponding to the inputs A, B and C with A as the MSB and C as the LSB.
     \begin{flushright}
      (EC 2017)
    \end{flushright}
    \item A function of Boolean variables $X, Y$ and $Z$ is expressed in terms of the minterms as $F(X,Y,Z)=\sum m(1,2,5,6,7)$ write $F$ in product of sum form.
    \begin{flushright}
      (EC 2015)
    \end{flushright}
    \item Given $F(P,Q,R)= PQ + Q\overline{R}+P\overline{R}$ 
   rewrite this $F$ in standard canonical form.
   \begin{flushright}
      (CS 2010)
    \end{flushright}
    \item Given $f_1, f_2$ and $f$ in canonical sum of products forms. $f_1(a,b,c,d)= \sum m(4,5,6,7,8)$, $f_3(a,b,c,d)= \sum m(1,6,15)$ and $f= \sum m(1,6,8,15)$. If $f=f_1f_2+f_3$ then $f_2$ is ?
     \begin{flushright}
      (CS 2008)
    \end{flushright}
    \item Consider three 4-variables functions $f_1, f_2$ and $f_3$, which are expressed in sum-of-minterms as $f_1 = \sum m(0,2,5,8,14)$, $f_2 = \sum m(2,3,6,8,14,15)$, and $f_3 = \sum m(2,7,11,14)$ express $f$ in sum-of-minterms if $f=(f_1\cdot f_2 )\bigoplus f_3$.
    \begin{flushright}
      (CS 2019)
    \end{flushright}
    \item $f(A,B,C,D) = \prod M(0,1,3,4,5,7,9,11,12,13,14,15)$ is a Maxterm representation of a Boolean function $f(A,B,C,D)$ where A is the MSB and D is the LSB. Write the equivalent minized Minterm representation of this function.\begin{flushright}
      (EE 2015)
    \end{flushright}
\end{enumerate}
\end{document}
